A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2025-02-16 manuscript/manuscript.qmd
changed phrasing to estimand differences

Another common challenge in the emulation of oncology trials is the estimation of an "intention-to-treat" (ITT) analogous estimand which is usually the primary estimand reported in oncology RCTs. Due to intercurrent events, such as non-adherence or the crossover of a high proportion of patients from the control to the intervention arm, trial emulation are prone to be biased towards the null. Although this is also a common challenge in the analysis of RCTs,[@rufibach2018] treatment protocols in routine care are often observed to be less stringent compared to trials.[@merola2024calibrating] In order to derive comparable estimands it is therefore crucial to understand and contextualize the proportion and timing of treatment switching and discontinuation in both the trial and its emulation.

>>>>

Another common challenge in the emulation of oncology trials is the estimation of an "intention-to-treat" (ITT) analogous estimand which is usually the primary estimand reported in oncology RCTs. Due to intercurrent events, such as non-adherence, crossover of a high proportion of patients from the control to the intervention arm, or differences in subsequent therapy lines there may be estimand differences between trial and emulation.[@manitz2022estimands] Although this is also a common challenge in the analysis of RCTs,[@rufibach2018] treatment protocols in routine care are often observed to be less stringent compared to trials.[@merola2024calibrating] In order to derive comparable estimands it is therefore crucial to understand and contextualize the proportion and timing of treatment switching and discontinuation in both the trial and its emulation.
